Figures

### 2023-03-06 figures/figures.Rmd
rm extra space
print distances

```{r, echo=FALSE}
if(dir.exists("../scripts")){
    shim <- "../"
    source("../scripts/99_utils.R")
}else{
    shim <- ""
    source("scripts/99_utils.R")
}

```

@@

dt_dist <- unlist(st_distance(coords_ire, dt_sites))
dt_sites_close <- dt_sites[dt_dist < units::as_units(100, "mi"),]

>>>>

```{r, echo=FALSE}
if(dir.exists("../scripts")){
    shim <- "../"
    source("../scripts/99_utils.R")
}else{
    shim <- ""
    source("scripts/99_utils.R")
}
```

@@

dt_sites$dist <- unlist(list(unlist(st_distance(coords_ire, dt_sites)))) / 1609.34
dt_sites_close <- dt_sites[dt_sites$dist < 100,]
head(dplyr::arrange(dt_sites_close, dist)$dist)
